---
title: 'US Accidents (2016-2021) or: What the hell is going on in California?'
author: "Seth Buesing, Jason White, Kai Yamanishi"
output: 
  html_document:
    keep_md: TRUE
    toc: TRUE
    toc_float: TRUE
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for data cleaning and plotting
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(shiny)         # for creating interactive apps
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
library(osmdata)
library(reticulate)
theme_set(theme_minimal())
```

#Introduction
  In our search for an interesting dataset to analyze we came across a wonderfully organized table detailing traffic accidents in the contiguous United States over the last 5 years. What caught our interest in specific was looking at the evolution over time of crash statistics in specific states- most notably California. As the graph below shows, the number of accidents in California has been doubling each year, and we wanted to figure out just what was happening. The dataset we're working with is extraordinarily large, containing over 2.8 million accidents taken from automated traffic sensors and logged reports. Each accident has 47 columns of information.

*Insert Graph 1 from Jason*

#Data Collection
  Our Data Collection process was pretty simple- we found the data set on [https://www.kaggle.com/datasets/sobhanmoosavi/us-accidents]() and downloaded the csv file. We did run into some issues using this csv, however due to its sheer size (1.1 GB).

#Analysis



```{r, cache = TRUE}
  accidents_data <- read_csv("local/US_Accidents_Dec21_updated.csv")
```  
  
```{r, cache = TRUE}
big_streets <- opq(bbox = c(-118.965,33.6818,-117.3367,34.4395), timeout = 100)%>%
  add_osm_feature(key = "highway", 
                  value = c("motorway", "primary", "motorway_link", "primary_link")) %>%
  osmdata_sf()
```

```{r, cache = TRUE}
  thoroughfares <- opq(bbox = c(-118.965,33.6818,-117.3367,34.4395), timeout = 100)%>%
  add_osm_feature(key = "highway", 
                  value = c("motorway")) %>%
  osmdata_sf()
```